From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks

### 2018-04-26 article/article.tex
Fixed overlapping experiment
Changes to indexer
more changes to article and updated query set aulity analysis

\DeclareMathOperator*{\argmax}{argmax}

\date{Received: date / Accepted: date}

@@

@@

\begin{figure*}[ht]
\includegraphics[width=\textwidth]{images/ppi_example_combined.eps}
\caption{An example of the GO term \textit{``SNAP receptor activity''} (16 nodes) on the \textit{Arabidopsis thaliana} protein-protein interaction network.
(A) Shows the full network with 3 randomly chosen query nodes from the full query set.
(B) Shows a reduced view of the network where a threshold is selected, reducing the network to 404 nodes.
(C) Shows an example ROC curve, sampled from combinations of using 3 randomly selected query nodes including this term.
Blue nodes indicate those in the randomly selected 3 query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
}
\label{fig:query_example}
\end{figure*}

@@

\bibliographystyle{IEEEtran} 
\bibliography{references}

>>>>

@@

\begin{figure*}[ht]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_overlap_auc_1000.eps}
        \caption{1000 nodes}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/lfr_binary_overlap_auc_1000.eps}
        \caption{5000 nodes}
    \end{subfigure}
    \caption{Overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
     Data points represent mean auc scores for all communities on 100 sampled networks at varying overlapping fraction of nodes.
     Error bars represent standard deviations.}
\end{figure*}

@@

\begin{figure*}[ht]
\includegraphics[width=\textwidth]{images/ppi_example_combined.eps}
\caption{An example of the GO term \textit{``SNAP receptor activity''} (16 nodes) on the \textit{Arabidopsis thaliana} protein-protein interaction network.
(A) Shows the full network with 3 randomly chosen query nodes from the full query set.
(B) Shows a reduced view of the network where a threshold is selected, reducing the network to 404 nodes.
Blue nodes indicate those in the randomly selected 3 query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
(C) Shows an example ROC curve from the cross validation described in the main text. 
Based on 3 randomly selected query nodes containing this GO term.
}
\label{fig:query_example}
\end{figure*}

@@

\bibliographystyle{acm} 
\bibliography{references}
